Assessment of Fire Fighter Steam Burn Potential by Quantifying Water Vapor Transfer in Protective Ensemble

### 2015-01-13 Projects/Exploratory_Steam/Supporting_Material/FRD_PML_SoW.tex
Steam: minor edit to SoW, add experimental data and plotting script

\begin{table}
\centering
\captionof{table}{Exposure Tests}\label{tab:tests}
\begin{tabular}{lllll}
\toprule[1.5pt]
Series \#       &  Material                   &  Duration       &  Environment       &  Reps  \\
\midrule
1               &  None                       &  Steady-State   &  Peak T \& RH   &  5  \\[.25cm]
2               &  Full PPE (3 layer sample)  &  10~min$^*$     &  Peak T \& RH   &  5  \\[.25cm]
3               &  Woven Fabric (hood)        &  10~min$^*$     &  Peak T \& RH   &  5  \\[.25cm]
4               &  None                       &  Steady-State   &  Min T \& RH    &  5 \\[.25cm]
5               &  Full PPE (3 layer sample)  &  10~min$^*$     &  Min T \& RH    &  5  \\[.25cm]
6               &  Woven Fabric (hood)        &  10~min$^*$     &  Min T \& RH    &  5 \\[.25cm]
7$^+$           &  None                       &  Steady-State   &  Mid T \& RH    &  5 \\[.25cm]
8$^+$           &  Full PPE (3 layer sample)  &  10~min$^*$     &  Mid T \& RH    &  5 \\[.25cm]
9$^+$           &  Woven Fabric (hood)        &  10~min$^*$     &  Mid T \& RH    &  5 \\[.25cm]
\bottomrule[1.25pt]
\end{tabular}
\footnotesize
\raggedright
\\ $^*$ 10 min for first replicate. Adjust as necessary.
\\ $^+$ If necessary
\normalsize
\end{table}

>>>>

\begin{table}
\centering
\captionof{table}{Exposure Tests}\label{tab:tests}
\begin{tabular}{lllll}
\toprule[1.5pt]
Test \#       &  Material                   &  Duration       &  Environment       &  Reps  \\
\midrule
1               &  None                       &  Steady-State   &  85~$^{\circ}$C \& 95~\%RH   &  5  \\[.25cm]
2               &  Full PPE (3 layer)         &  10~min$^*$     &  85~$^{\circ}$C \& 95~\%RH   &  5  \\[.25cm]
3               &  Woven Fabric (hood)        &  10~min$^*$     &  85~$^{\circ}$C \& 95~\%RH   &  5  \\[.25cm]
4               &  None                       &  Steady-State   &  85~$^{\circ}$C \& 65~\%RH    &  5 \\[.25cm]
5               &  Full PPE (3 layer)         &  10~min$^*$     &  85~$^{\circ}$C \& 65~\%RH    &  5  \\[.25cm]
6               &  Woven Fabric (hood)        &  10~min$^*$     &  85~$^{\circ}$C \& 65~\%RH    &  5 \\[.25cm]
7$^+$           &  None                       &  Steady-State   &  85~$^{\circ}$C \& 35~\%RH    &  5 \\[.25cm]
8$^+$           &  Full PPE (3 layer)         &  10~min$^*$     &  85~$^{\circ}$C \& 35~\%RH    &  5 \\[.25cm]
9$^+$           &  Woven Fabric (hood)        &  10~min$^*$     &  85~$^{\circ}$C \& 35~\%RH   &  5 \\[.25cm]
\bottomrule[1.25pt]
\end{tabular}
\footnotesize
\raggedright
\\ $^*$ 10 min for first replicate. Adjust as necessary.
\\ $^+$ If necessary
\normalsize
\end{table}
